---
title: "Data Sharing Analysis"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This document analyzes the rate of data sharing among authors. The focus is on comparing the number of authors who share their data fully with those who include data only in the article but do not share the underlying datasets.

# Data Preparation

In this section we simulate a dataset. In a real analysis, replace the simulated data with your actual dataset.

```{r data-preparation}
# Simulated data
# We assume a variable "sharing_type" where:
# "Fully Shared" indicates full data sharing by the author
# "Data in Article" indicates data only present within the article

set.seed(123)
n <- 200  # total number of authors
sharing_types <- sample(
  c("Fully Shared", "Data in Article"), n, replace = TRUE,
  prob = c(0.6, 0.4)
)
data <- data.frame(
  author_id = 1:n,
  sharing_type = sharing_types
)

head(data)
```

# Descriptive Statistics

Here we compute the count and rate of each type of data sharing.

```{r descriptive-stats}
library(dplyr)

# Count the occurrences of each sharing type
sharing_summary <- data %>%
  group_by(sharing_type) %>%
  summarise(
    count = n()
  ) %>%
  mutate(
    rate = count / sum(count)
  )

sharing_summary
```

# Visualization

We can create a bar plot to visualize the difference in rates between authors who fully share data versus those who include data only in the article.

```{r visualization, fig.height=5, fig.width=7}
library(ggplot2)

ggplot(sharing_summary, aes(x = sharing_type, y = count, fill = sharing_type)) +
  geom_bar(stat = "identity", width = 0.5) +
  labs(
    title = "Rate of Data Sharing Among Authors",
    x = "Sharing Type",
    y = "Count of Authors"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

# Conclusion

The analysis provides a snapshot of data sharing practices among authors. It allows us to quickly compare the number of authors who share data fully versus those who
 embed data only within the article. This approach can be easily extended to include more detailed analyses, such as trends over time, discipline-specific rates, 
and the impact of open data policies.